The problem and promise of scale in animal social multilayer networks

### 2020-02-08 paper/manuscript.Rmd
network metrics reshuffle/clarifications

### Network metrics
<!-- TODO: expand + simplify + examples individual A, B etc -->
We used a series of metrics to characterize the multilayer networks, focusing on
the the role of individuals, relevance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated the graph
strength, degree weighted by the values of the edge, for each individual for
each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Degree centrality, the number of direct connections an individual
has to other individuals in the network, is the basis of many calculations
[@Kivela_2014]. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and neighbourhood,
we measured the connective redundancy, the proportion of neighbours repeated in
multiple layers, and the layer relevance, the proportion of neighbours present
in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].

>>>>

### Network metrics
<!-- TODO: expand + simplify + examples individual A, B etc -->
We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers and the similarity
of different layers. To measure the role of individuals, we calculated degree centrality and graph strength. Degree centrality is the number of direct connections an individual has to other individuals in a network layer. Graph strength is the degree weighted by the strength of association, in this case SRI, in each layer-specific season and landcover context <!-- TODO: citation for graph
strength?-->. Extending degree centrality, we calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. We evaluated the relevance and redundancy of layers by combining the multidegree and neighbourhood to calculate connective redundancy and layer relevance. Connective redundancy is the proportion of neighbours repeated in multiple layers, and layer relevance is the proportion of neighbours present in each layer compared to the neighbourhood for each individual
[@Berlingerio_2012].  Finally, we calculated the similarity of layers between
seasons, across landcover classes (e.g.: winter open compared to summer open)
using the Pearson correlation coefficient [@Br_dka_2018].

<!-- TODO: EVW "parallelism"? -->
